\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{geometry}
\geometry{margin=1in}
\title{Mademarket + CoreSignal Enrichment Pipeline}
\author{}
\date{\today}

\begin{document}

\maketitle

\section{Overview}
This pipeline automates the process of pulling, segmenting, and enriching recipient data from the Mademarket API with company and person-level data from CoreSignal. Outputs are organized for easy access and further analysis.

\section{Mademarket API Data Pull}
\begin{itemize}
  \item \textbf{Script:} \texttt{Made\_Market/MadeMarket\_Pull.py}
  \item \textbf{Function:} Pulls recipient data for a specified distribution and segments into opened/unopened.
  \item \textbf{How to run:}
\begin{lstlisting}[language=bash]
python Made_Market/MadeMarket_Pull.py
\end{lstlisting}
  \item \textbf{Outputs:}
  \begin{itemize}
    \item \texttt{Made\_Market\_Data/mademarket\_2025\_ISTE.csv}
    \item \texttt{Made\_Market\_Data/opened/mademarket\_2025\_ISTE\_opened.csv}
    \item \texttt{Made\_Market\_Data/unopened/mademarket\_2025\_ISTE\_unopened.csv}
  \end{itemize}
\end{itemize}

\section{Company Enrichment (CoreSignal)}
\begin{itemize}
  \item \textbf{Script:} \texttt{coresignal\_enrichment/Company\_Enrich.py}
  \item \textbf{Function:} Enriches each recipient with company data from CoreSignal using the email domain.
  \item \textbf{How to run:}
\begin{lstlisting}[language=bash]
python coresignal_enrichment/Company_Enrich.py --input Made_Market_Data/opened/mademarket_2025_ISTE_opened.csv --output coresignal_enrichment/company_enriched/opened_enriched.csv
\end{lstlisting}
  \item \textbf{Outputs:}
  \begin{itemize}
    \item \texttt{coresignal\_enrichment/company\_enriched/opened\_enriched.csv}
    \item \texttt{coresignal\_enrichment/company\_enriched/unopened\_enriched.csv}
  \end{itemize}
\end{itemize}

\section{Person Enrichment (CoreSignal)}
\begin{itemize}
  \item \textbf{Script:} \texttt{coresignal\_enrichment/Person\_Enrich.py}
  \item \textbf{Function:} Attempts to enrich each recipient with person-level data from CoreSignal using available information (email, first/last name, company name).
  \item \textbf{How to run:}
\begin{lstlisting}[language=bash]
python coresignal_enrichment/Person_Enrich.py --input Made_Market_Data/opened/mademarket_2025_ISTE_opened.csv --output coresignal_enrichment/person_enriched/opened_enriched.csv
\end{lstlisting}
  \item \textbf{Outputs:}
  \begin{itemize}
    \item \texttt{coresignal\_enrichment/person\_enriched/opened\_enriched.csv}
    \item \texttt{coresignal\_enrichment/person\_enriched/unopened\_enriched.csv}
  \end{itemize}
\end{itemize}

\section{Output Directory Structure}
\begin{verbatim}
prospectindata/
  Made_Market_Data/
    mademarket_2025_ISTE.csv
    opened/
      mademarket_2025_ISTE_opened.csv
    unopened/
      mademarket_2025_ISTE_unopened.csv
  coresignal_enrichment/
    company_enriched/
      opened_enriched.csv
      unopened_enriched.csv
    person_enriched/
      opened_enriched.csv
      unopened_enriched.csv
\end{verbatim}

\section{Notes on Person Enrichment}
\begin{itemize}
  \item The pipeline preprocesses recipient emails to extract first/last names and company names for enrichment.
  \item \textbf{Limitation:} CoreSignal rarely has emails for individuals; name and company must match their public professional profile for a successful enrichment.
  \item \textbf{Current status:} Despite preprocessing, individual-level data is not consistently populated. Raahul has previously had this working and will take ownership of further refinement.
\end{itemize}

\section{How to Run the Full Pipeline}
\begin{enumerate}
  \item Pull and segment Mademarket data:
\begin{lstlisting}[language=bash]
python Made_Market/MadeMarket_Pull.py
\end{lstlisting}
  \item Enrich with company data:
\begin{lstlisting}[language=bash]
python coresignal_enrichment/Company_Enrich.py --input Made_Market_Data/opened/mademarket_2025_ISTE_opened.csv --output coresignal_enrichment/company_enriched/opened_enriched.csv
\end{lstlisting}
  \item Enrich with person data:
\begin{lstlisting}[language=bash]
python coresignal_enrichment/Person_Enrich.py --input Made_Market_Data/opened/mademarket_2025_ISTE_opened.csv --output coresignal_enrichment/person_enriched/opened_enriched.csv
\end{lstlisting}
\end{enumerate}

\section{Handoff and Next Steps}
\begin{itemize}
  \item The pipeline is modular, robust, and well-logged.
  \item Company enrichment is working and outputs are as expected.
  \item Person enrichment is set up and ready for further refinement by Raahul or others with more experience on the CoreSignal person API.
  \item All scripts are documented and can be run independently for testing or troubleshooting.
\end{itemize}

\end{document} 